Z-Resonance at LEP

### 2010-08-04 Z0-Publikation/tex/paper-template.tex
nur noch kontrolllesen faellig

The detector for all of these particles is LEP. Its structure can be seen
in \fref{aufbau}.
\begin{figure}[htb]
 \centering
 \includegraphics[page=5,viewport=286 620 508 765,clip,%
  width=\columnwidth,keepaspectratio]{../../Z0/docs/Z0ResFprakt}
 \caption{design of the L3 detector.}
 \todo[inline]{soll hier eine quelle hin?}
 \label{fig:aufbau}
\end{figure}
There are layers of components with different purposes, starting from the
interaction point, these are the tracking chamber, the electromagnetic calorimeter,
the hadronic calorimeter and finally the muon chamber.

@@

\begin{table}[h]
\begin{center}
\begin{tabular}{|l|l|l|}
\hline
energy $\sqrt{s}$ [\si{\GeV}] & hadronic events & cross section $σ_0^{\mathrm{had}}$ [\si{\nano\barn}]\\
\hline
89.48 & 1848 ± 43 ± 52 & 10.55 ± 0.18 ± 0.16 \\
91.33 & 3980 ± 63 ± 79 & 29.98 ± 0.49 ± 0.43 \\
93.02 & 2149 ± 46 ± 51 & 14.56 ± 0.24 ± 0.24 \\
\hline
\end{tabular}
\vspace*{0.3cm}
\caption{\baselineskip=0.38cm analyzed hadronic events at different center of mass energies.}
\label{tab:hadr_events}
\end{center}
\vspace*{-0.5cm}
\end{table}

@@

\section{ Summary}
In order to sum up the results one has to say that this is a very precise
confirmation of the predictions of the standard model. The first exact
measurement of the weak mixing angle was done, which was one of the most important
tasks of this experiment.

\begin{thebibliography}{}
\baselineskip=0.38cm
\bibitem{z1} T. H. Bauer et al., Rev. Mod. Phys. \textbf{50} No 2 (1978) 261  
\bibitem{z2}D. Schildknecht et al., Phys. Lett. \textbf{B 449} (1999) 328
\bibitem{z3}A. Donnachie, P. V. Landshoff, Phys. Lett. \textbf{B 478} (2000) 146

>>>>

The detector for all of these particles is LEP. Its structure can be seen
in \fref{aufbau}.
\begin{figure}[htb]
 \centering
 \includegraphics[page=5,viewport=286 620 508 765,clip,%
  width=\columnwidth,keepaspectratio]{../../Z0/docs/Z0ResFprakt}
 \caption{design of the L3 detector \cite{pic}.}
 \todo[inline]{soll hier eine quelle hin?}
 \label{fig:aufbau}
\end{figure}
There are layers of components with different purposes, starting from the
interaction point, these are the tracking chamber, the electromagnetic calorimeter,
the hadronic calorimeter and finally the muon chamber.

@@

\begin{table}[h]
\begin{center}
\begin{tabular}{|l|l|l|}
\hline
energy $\sqrt{s}$ [\si{\GeV}] & hadronic events & cross section
$σ^{\mathrm{had}}$ [\si{\nano\barn}]\\
\hline
89.48 & 1848 ± 43 ± 52 & 10.55 ± 0.18 ± 0.16 \\
91.33 & 3980 ± 63 ± 79 & 29.98 ± 0.49 ± 0.43 \\
93.02 & 2149 ± 46 ± 51 & 14.56 ± 0.24 ± 0.24 \\
\hline
\end{tabular}
\vspace*{0.3cm}
\caption{\baselineskip=0.38cm analyzed hadronic events at different center of mass energies.}
\label{tab:hadr_events}
\end{center}
\vspace*{-0.5cm}
\end{table}

@@

\section{ Summary}
In order to sum up the results one has to say that this is a very precise
confirmation of the predictions of the standard model. The properties of the
predicted $Z^0$-boson could be measured precisely. Additionally the first exact
measurement of the weak mixing angle was done successfully, which was one of the
most important tasks of this experiment.

It has to be mentioned that the background was found to be negligible and
therefore it was not included in the calculations. This could be done in a
further study. During the next months of data taking, there will also be higher
luminosities available as well as measurements at higher center of mass
energies, which will improve the resuls of this study.

\begin{thebibliography}{}
\baselineskip=0.38cm
\bibitem{pic} http://ams.pg.infn.it/ams-italy/pub/5\_5.htm
